\chapter{Conclusions}
%%%%%%%%%%%%%%%%%%%%%
The benefits of deploying a large number of robots in dynamic multi-tasking environment can not fully be realized without adopting an effective communication and sensing strategy for a given multi-robot system. This study has focused on comparing two bio-inspired  communication and sensing strategies in producing self-regulated MRTA by an interdisciplinary model of DOL, AFM. Under the GSNC strategy, AFM has produced the desired self-regulated MRTA among a group of 8 and 16 robots. This gives the evidence that AFM can successfully solve the MRTA issue of a complex multi-tasking environment like a manufacturing shop-floor. Under the LSLC strategy, AFM can also produce the desired self-regulated MRTA for 16 robots with different communication and sensing ranges.

From the comparative results, it can be concluded that for large group of robots,  degradation in  task-performance and task-specialization of robots are likely to occur  under GSNC strategy that relies upon a centralized communication system. Thus GSNC strategy can give better performance when the number of tasks and robots are relatively small. This confirms the assertions made by some biologists that self-regulated DOL among small group of individuals can happen without any significant amount of local communications and interactions. However, these findings suggest that task-specialization can still be beneficial among the individuals of a small group which contradicts the claim that small groups only posses the generalist workers, but not the specialists.

On the other hand, LSLC strategy is more suitable for large group of individuals that are likely to be unable to perform global sensing and global communications with all individuals of the group. The design of communication and sensing range is still remained as a critical research issue. However, these results suggest that the idea of maximizing information gain is not appropriate under a stochastic task-allocation process, as more information causes more task-switching behaviours that lowers the level of task-specialization of the group. This might not be the case under a deterministic task-allocation scheme where more information leads to better and optimum allocations, but that is limited to a small group of individuals. Nevertheless, despite having the limited communication and sensing range, LSLC strategy helps to produce comparatively better task-allocation with increased task-specialization and significantly reduced motions or savings in energy e.g. battery power.

This study has experienced all the major challenges of implementing a large multi-robot system within limited time and resource constraints. From these experiences it can be said that, by following flexible and open-source hardware and software platforms, it is possible to construct a large multi-robot system for conducting real-robotic experiments within limited time-frame. This is good news for those who want to test their models using a large real-robotic system without relying on simulation only. However in this case, one needs to adopt an appropriate test-driven bottom-up development approach, instead of following the traditional top-down ``model - simulate -  export-to-real-robots'' approach. 
%===================================================================
\section{Contributions}
The general contributions of this thesis are listed below.
\begin{itemize}
    \item \textbf{Self-organization: } 
Here it is found that self-organized allocation may produce specialized workers even when the group size is \textit{small} ($<$ 10), unlike assuming generalist workers prevents specialization in small groups \cite{Garnier+2007}.
    \item \textbf{Task-allocation: }
This study relates the selection of appropriate communication strategy with effective task-allocation of a large group of individuals. Here it is found that local communication in task-allocation may outperform centralized one in terms of energy usage.
\item \textbf{System development: }
This empirical study shows that bottom-up de-coupled construction of a fairly large artificial system yields higher advantages particularly, flexibility and integration with inter-operable elements.%in achieving self-regulated MRTA.
\end{itemize}
The specific contributions of this thesis are as follows:
\begin{itemize}
\item \textbf{Interpretation of AFM as a basic mechanism of self-regulated MRTA.} As discussed in Chapter \ref{afm}, AFM can be  interpreted in a multi-robot manufacturing shop-floor scenario.  In this process  the generic part of the model has been separated out, e.g. providing learning and forgetting rate, from the domain-specific part, e.g. defining task-urgency increase and decrease rate. Similar interpretations can also be made in other task-domains. This study can be used as a guide to any such future application of AFM.
%
\item \textbf{Validation of AFM through experiments with reasonably large number of real robots i.e. 16 e-puck robots.} It can be very difficult to realize an abstract model without having a practical example implementation of it. Mere computer simulation of a model can not be considered enough. In this thesis,  a rich implementation of AFM  have been provided with detail algorithms and links to source code. This implementation can be replicated in solving many real-world tasks and resource allocation problems, e.g. resource allocation in automation industries.
%
\item \textbf{Comparisons of the performances of two bio-inspired communication and sensing strategies in achieving self-regulated MRTA.} Since AFM has wrapped the communication and sensing of agents  in a system-wide continuous flow of information, one needs to instantiate an instance of communication system to provide an infrastructure for this information flow. In this study,  two well-known bio-inspired  communication and sensing strategies, GSNC and LSLC, have been tested and measured their impact on self-regulated MRTA of a fairly large group of robots. This comparison provides an overall understanding of information exchange strategies commonly found in various social systems.
%
\item \textbf{Development of a flexible multi-robot control architecture using D-Bus IPC technology.} In this thesis,  the foundation of a new kind of robot control architecture has been laid down that uses the state-of-the-art D-Bus IPC protocol for decoupling the communication among various software components of a large multi-robot system. This greatly helps to reduce the bottlenecks in developing many heterogeneous software components using different programming languages and software frameworks.
%
\item \textbf{Classification of MRTA solutions based on three major axes: organization of task-allocation, communication, interaction among robots.} This concise classification helps to remove the ambiguities among various MRTA solutions found in the literature.  It is very common to be confused with terminologies used by the MRTA solutions found in the existing body of literature. Many researchers claim that their MRTA solutions are decentralized. These claims do not explain fully in \textit{what} aspects those solutions are decentralized. Do they employ one or multiple task-allocators? Are the communications among robots decentralized? But these questions do not answer if all robots has their own task-allocation capabilities built into their controllers. Thus these ambiguities has motivated to explain the existing MRTA solutions in terms of three major axes as mentioned above. They can enable to precisely  explain the characteristics of most of the existing MRTA solutions and locate them within a tractable space. For example, by answering the question: \textit{``How many task-allocator does a MRTA solution propose?''} it can be confirmed that if this solution is fully distributed, centralized or semi-centralized. By using similar types of probes, one can find the characteristics of communication and interaction provided by a MRTA solution.
\end{itemize}
%================================================================
\section{Limitations}
In this study, the interactions among robots for task-completion  under manufacturing shop-floor scenario was kept as simple as possible. This was done mainly for minimizing the time and complexity of real-robotic implementation. However, in most of the instances of biological self-regulated DOL, e.g. among polybia wasps that follow LSLC strategies for DOL, several inter-dependent tasks are often performed concurrently with a high degree of interaction among individuals. 

In this study the validation of AFM was limited to a group of homogeneous robots that had initially same level of task-sensitization. Moreover no dynamic task was introduced during the run-time of the experiments. Due to the stochastic task-allocation process, it was always possible to see the  variation in task-urgencies. P2P communication among robot-controllers occurred in host-PC. The use of communication range was not validated using real-robotic hardware. 

In self-regulated MRTA experiments, two fixed communication ranges  were selected with an approximation of LSLC strategy. Some researchers addressed the issue of deciding the optimum communication range \cite{Yoshida+2000}. However, much research is required to find optimum communication range as a property of self-regulation of individuals. For example, in Sec. \ref{bg:bio-comm:comm-role}  it is seen that urgency of a task directly influences the communication behaviours of individuals, e.g. honey-bees modulate their dancing behaviours based on the quality of flower source. In this study, this issue has not been addressed.

\section{Future works}
This study can possibly be extended in co-operative task domains where different individuals with variety of task-skills should interact with each other directly. For example,  one can consider complex manufacturing shop-floor scenarios where the assembly of a machine part requires coordination among multiple tasks. 

AFM can be applied to a more challenging environment with suddenly appearing (and disappearing) dynamic tasks that can resemble to the real-world use-cases where any task can be pre-empted by other tasks. Moreover, some more research can be done in order to figure out how to optimize the initial experimental parameters, e.g. robots' task learning and forgetting rate. Real implementation of communication range can possibly be achieved by using suitable on-board communication module, e.g. Wifi, with  relatively powerful robots.

Finally, in terms of real-world implementation, AFM can be considered for solving challenging industrial automation tasks. For example, AFM can be applied in automated material handing tasks in ware-houses. In this way, this interdisciplinary model can help to overcome the existing challenges in the industry.